A Second Screen Architecture for Capturing Viewers' Interaction Data in TV Environments

### 2014-09-10 src/paper.tex
WIP: response in JSON format

Some of the HTTP requests

>>>>

Some of the HTTP requests were created only to add content to the web application, so that the client devices could access this content. The HTTP requests that use a GET method typically are used in the client devices to retrieve content from the web application. In this experiment, it was employed the JSON format to

\begin{figure}
\begin{verbatim}
{
    id: 5722646637445120,
    viewer: {
        id: 5629499534213120,
        username: "user1"
    },
    program: {
        id: 5649391675244544,
        videoCode: "ZuQ4obQAN8",
        title: "A Program Title"
    },
    rating: 4
}
\end{verbatim}
\caption{Example of response to an HTTP request in JSON format.}
\label{fig_response_json}
\end{figure}
